\documentclass[journal,9pt,onecolumn]{IEEEtran}
\usepackage[a5paper, margin=8mm]{geometry}
%\usepackage{lmodern} % Ensure lmodern is loaded for pdflatex
\usepackage{tfrupee} % Include tfrupee package

\setlength{\headheight}{1cm} % Set the height of the header box
\setlength{\headsep}{0mm}     % Set the distance between the header box and the top of the text

\usepackage{gvv-book}
\usepackage{gvv}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{txfonts}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{gensymb}
\usepackage{comment}
\usepackage[breaklinks=true]{hyperref}
\usepackage{tkz-euclide} 
\usepackage{listings}
% \usepackage{gvv}                                        
\def\inputGnumericTable{}                                 
\usepackage[latin1]{inputenc}                                
\usepackage{color}                                            
\usepackage{array}                                            
\usepackage{longtable}                                       
\usepackage{calc}                                             
\usepackage{multirow}                                         
\usepackage{hhline}                                           
\usepackage{ifthen}                                           
\usepackage{lscape}
\begin{document}

\bibliographystyle{IEEEtran}
\vspace{3cm}
\title{2015-ME-27-39}
\author{AI24BTECH11002 - K. Akshay Teja}
\maketitle
 %\newpage
 \bigskip
{\let\newpage\relax\maketitle}

\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\setlength{\intextsep}{10pt} % Space between text and floats

\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\renewcommand{\thetable}{\theenumi}


\begin{enumerate}
\setcounter{enumi}{26}
% Question 27
\item Consider a steel (Young's modulus $E = 200$ GPa) column hinged on both sides. Its height is $1.0$ m and cross-section is $10$ mm $\times$ $20$ mm. The lowest Euler critical buckling load (in N) is


% Question 28
\item A swimmer can swim $10$ km in $2$ hours when swimming along the flow of a river. While swimming against the flow, she takes $5$ hours for the same distance. Her speed in still water (in km/h) is


% Question 29
\item Which one of the following is the most conservative fatigue failure criterion?
\begin{multicols}{4}
\begin{enumerate}
    \item Soderberg
    \item Modified Goodman
    \item ASME Elliptic
    \item Gerber
\end{enumerate}
\end{multicols}

% Question 30
\item Which one of the following types of stress-strain relationship best describes the behaviour of brittle materials, such as ceramics and thermosetting plastics, $(\sigma =$ stress and  $\varepsilon =$ strain)?

\begin{multicols}{2}
\begin{enumerate}
    \item \input{figs/fig.tex}
    \item \input{figs/fig2.tex}
    \item \input{figs/fig3.tex}
    \item \input{figs/fig4.tex}
\end{enumerate}
\end{multicols}




% Question 31
\item Match the following products with preferred manufacturing processes:
\begin{table}[h!]
    \centering
    \input{tables/table.tex}
    \label{tab:ME-2015}
\end{table}
\begin{multicols}{4}
\begin{enumerate}
    \item P-4, Q-3, R-1, S-2
    \item P-4, Q-3, R-2, S-1
    \item P-2, Q-4, R-3, S-1
    \item P-3, Q-4, R-2, S-1
\end{enumerate}
\end{multicols}


% Question 32
\item Holes of diameter $25.0^{+0.040}_{-0.020}$ mm are assembled interchangeably with the pins of diameter $25.0^{+0.005}_{-0.008}$ mm. The minimum clearance in the assembly will be

\begin{multicols}{4}
\begin{enumerate}
    \item $0.048$ mm
    \item $0.015$ mm
    \item $0.005$ mm
    \item $0.008$ mm
\end{enumerate}
\end{multicols}
    
% Question 33
\item Under certain cutting conditions, doubling the cutting speed reduces the tool life to $\brak
{\frac{1}{16}}^{th}$ of the original. Taylor's tool life index $\brak{n}$ for this tool-workpiece combination will be 



    
% Question 34
\item In a linear arc welding process, the heat input per unit length is inversely proportional to

\begin{multicols}{2}
\begin{enumerate}
    \item welding current
    \item welding voltage
    \item welding speed
    \item duty cycle of the power source
\end{enumerate}
\end{multicols}



% Question 35
\item The function of interpolator in a CNC machine controller is to

\begin{enumerate}
    \item control spindle speed
    \item coordinate feed rates of axes
    \item control tool rapid approach speed
    \item perform Miscellaneous (M) functions (tool change, coolant control etc.)
\end{enumerate}

% Question 36
\item Consider a spatial curve in three-dimensional space given in parametric form by$$
x\brak{t} = \cos t, \, y\brak{t} = \sin t, \, z\brak{t} = \frac{2}{\pi}t, \, 0 \leq t \leq \frac{\pi}{2}
$$

The length of the curve is

% Question 37
\item Consider an ant crawling along the curve $\brak{x - 2}^2 + y^2 = 4$, where $x$ and $y$ are in meters. The ant starts at the point $\brak{4, 0}$ and moves counter-clockwise with a speed of $1.57$ meters per second. The time taken by the ant to reach the point $\brak{2, 2}$ is (in seconds)



% Question 38
\item Find the solution of $\frac{d^2 y}{dx^2} = y$ which passes through the origin and the point $\brak{\ln 2, \frac{3}{4}}$

\begin{multicols}{4}
\begin{enumerate}
    \item $y = \frac{1}{2} e^x - e^{-x}$
    \item $y = \frac{1}{2}\brak{e^x + e^{-x}}$
    \item $y = \frac{1}{2}\brak{e^x - e^{-x}}$
    \item $y = \frac{1}{2} e^x + e^{-x}$
\end{enumerate}
\end{multicols}



    
% Question 39
\item The probability of obtaining at least two "SIX" in throwing a fair dice $4$ times is
\begin{multicols}{4}
\begin{enumerate}
    \item $\frac{425}{432}$
    \item $\frac{19}{144}$
    \item $\frac{13}{144}$
    \item $\frac{125}{432}$
\end{enumerate}
\end{multicols}
\end{enumerate}
\end{document}

