\documentclass[journal,9pt,onecolumn]{IEEEtran}
\usepackage[a5paper, margin=8mm]{geometry}
%\usepackage{lmodern} % Ensure lmodern is loaded for pdflatex
\usepackage{tfrupee} % Include tfrupee package

\setlength{\headheight}{1cm} % Set the height of the header box
\setlength{\headsep}{0mm}     % Set the distance between the header box and the top of the text

\usepackage{gvv-book}
\usepackage{gvv}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{txfonts}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{gensymb}
\usepackage{comment}
\usepackage[breaklinks=true]{hyperref}
\usepackage{tkz-euclide} 
\usepackage{listings}
% \usepackage{gvv}                                        
\def\inputGnumericTable{}                                 
\usepackage[latin1]{inputenc}                                
\usepackage{color}                                            
\usepackage{array}                                            
\usepackage{longtable}                                       
\usepackage{calc}                                             
\usepackage{multirow}                                         
\usepackage{hhline}                                           
\usepackage{ifthen}                                           
\usepackage{lscape}
\begin{document}

\bibliographystyle{IEEEtran}
\vspace{3cm}
\title{2018-ME-1-13}
\author{AI24BTECH11002 - K. Akshay Teja}
\maketitle
 %\newpage
 \bigskip
{\let\newpage\relax\maketitle}

\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\setlength{\intextsep}{10pt} % Space between text and floats

\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\renewcommand{\thetable}{\theenumi}


\begin{enumerate}

% Question 1
\item "Going by the \_\_\_\_\_, that many hands make light work, the school \_\_\_\_\_ involved all the students in the task."

The words that best fill the blanks in the above sentence are: \hfill \brak{2018}

\begin{multicols}{2}
\begin{enumerate}
    \item principle, principal
    \item principal, principle
    \item principle, principle
    \item principal, principal
\end{enumerate}
\end{multicols}

% Question 2
\item "Her \_\_\_\_\_ should not be confused with miserliness; she is ever willing to assist those in need."

The word that best fills the blank in the above sentence is: \hfill \brak{2018}

\begin{multicols}{4}
\begin{enumerate}
    \item cleanliness
    \item punctuality
    \item frugality
    \item greatness
\end{enumerate}
\end{multicols}


% Question 3
\item Seven machines take 7 minutes to make 7 identical toys. At the same rate, how many minutes would it take for 100 machines to make 100 toys? \hfill \brak{2018}

\begin{multicols}{4}
\begin{enumerate}
    \item 1
    \item 7
    \item 100
    \item 700
\end{enumerate}
\end{multicols}


% Question 4
\item A rectangle becomes a square when its length and breadth are reduced by 10 m and 5 m, respectively. During this process, the rectangle loses 650 m$^2$ of area. What is the area of the original rectangle in square meters?
\hfill \brak{2018}
\begin{multicols}{4}
\begin{enumerate}
    \item 1125
    \item 2250
    \item 2924
    \item 4500
\end{enumerate}
\end{multicols}

% Question 5
\item A number consists of two digits. The sum of the digits is 9. If 45 is subtracted from the number, its digits are interchanged. What is the number? \hfill \brak{2018}

\begin{multicols}{4}
\begin{enumerate}
    \item 63
    \item 72
    \item 81
    \item 90
\end{enumerate}
\end{multicols}

% Question 6
\item For integers $a$, $b$, and $c$, what would be the minimum and maximum values respectively of $a + b + c$ if $\log \abs{a} + \log \abs{b} + \log \abs{c} = 0$?\hfill \brak{2018}

\begin{multicols}{4}
\begin{enumerate}
    \item -3 and 3
    \item -1 and 1
    \item -1 and 3
    \item 1 and 3
\end{enumerate}
\end{multicols}

% Question 7
\item Given that $a$ and $b$ are integers and $a + a^2 b^3$ is odd, which one of the following statements is correct? \hfill \brak{2018}

\begin{multicols}{2}
\begin{enumerate}
    \item $a$ and $b$ are both odd
    \item $a$ and $b$ are both even
    \item $a$ is even and $b$ is odd
    \item $a$ is odd and $b$ is even
\end{enumerate}
\end{multicols}


% Question 8
\item From the time the front of a train enters a platform, it takes 25 seconds for the back of the train to leave the platform, while traveling at a constant speed of 54 km/h. At the same speed, it takes 14 seconds to pass a man running at 9 km/h in the same direction as the train. What is the length of the train and that of the platform in meters, respectively? \hfill \brak{2018}

\begin{multicols}{4}
\begin{enumerate}
    \item 210 and 140
    \item 162.5 and 187.5
    \item 245 and 130
    \item 175 and 200
\end{enumerate}
\end{multicols}

    
% Question 9
\item Which of the following functions describe the graph shown in the below figure? \hfill \brak{2018}
\begin{center}
    \input{figs/fig.tex}
\end{center}
\begin{multicols}{4}
\begin{enumerate}
    \item $y = \abs{x} + 1 - 2$
    \item $y = \abs{x - 1} - 1$
    \item $y = \abs{x} + 1 - 1$
    \item $y = \abs{x - 1} - 1$
\end{enumerate}
\end{multicols}

% Question 10
\item Consider the following three statements:

(i) Some roses are red. \\
(ii) All red flowers fade quickly. \\
(iii) Some roses fade quickly.

Which of the following statements can be logically inferred from the above statements?
\hfill \brak{2018}
\begin{enumerate}
    \item If (i) is true and (ii) is false, then (iii) is false.
    \item If (i) is true and (ii) is false, then (iii) is true.
    \item If (i) and (ii) are true, then (iii) is true.
    \item If (i) and (ii) are false, then (iii) is false.
\end{enumerate}


% Question 11
\item Four red balls, four green balls, and four blue balls are put in a box. Three balls are pulled out of the box at random one after another without replacement. The probability that all the three balls are red is \hfill \brak{2018}

\begin{multicols}{4}
\begin{enumerate}
    \item $\frac{1}{72}$
    \item $\frac{1}{55}$
    \item $\frac{1}{36}$
    \item $\frac{1}{27}$
\end{enumerate}
\end{multicols}


% Question 12
\item The rank of the matrix  $\begin{bmatrix}
-4 & 1 & -1 \\
-1 & -1 & -1 \\
7 & -3 & 1 \\
\end{bmatrix}$ is \hfill \brak{2018}

\begin{multicols}{4}
\begin{enumerate}
    \item 1
    \item 2
    \item 3
    \item 4
\end{enumerate}
\end{multicols}


% Question 13
\item According to the Mean Value Theorem, for a continuous function $f(x)$ in the interval $[a, b]$, there exists a value $\xi$ in this interval such that  $\int_a^b f(x) \, dx = $
\hfill \brak{2018}
\begin{multicols}{4}
\begin{enumerate}
    \item $f(\xi)(b-a)$
    \item $f(b)(\xi - a)$
    \item $f(a)(b - \xi)$
    \item 0
\end{enumerate}
\end{multicols}

\end{enumerate}
\end{document}
